---
output:
  pdf_document: default
  html_document: default
---
```{r, message = FALSE}
library(tidyverse)
library(car)
library(ggeffects)
```

```{r, message = FALSE}
#importing datasets from tidytuesday

tuition_cost <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-10/tuition_cost.csv')

salary_potential <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-10/salary_potential.csv')

diversity_school <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-10/diversity_school.csv') %>%
  select("name", "total_enrollment") %>%
  distinct()
```

```{r}
#creating our desired dataset

full_data <- full_join(tuition_cost, salary_potential, by = "name") %>%
  full_join(diversity_school, by = "name") %>%
  #merging the three datasets by school name
  drop_na(name, type, out_of_state_total, mid_career_pay, total_enrollment) %>%
  #removing any schools that do not have available the data we want
  mutate("ivy_league" = ifelse(name %in% c("Brown University", "Cornell University", "Dartmouth College", "Columbia University", "Yale University", "Harvard College", "University of Pennsylvania", "Princeton University"), "1", "0")) %>%
  #creating an indicator variable to designate whether a school is an ivy league or not
  mutate("tuition_avg" = (in_state_total + out_of_state_total)/2)
#creating a tuition average variable by finding the mean instate and out of state tuitions
```

```{r}
#writing as a csv to share
write_csv(full_data, file = "college_scoreboard.csv")
```


### First Model (MLR)

```{r}
#matrix plot to check for relationships
pairs(mid_career_pay ~ tuition_avg + factor(type) + total_enrollment + factor(ivy_league), data = full_data)
#first model with untransformed data
college1_mlr <- lm(mid_career_pay ~ tuition_avg + type + total_enrollment + ivy_league, data = full_data)
summary(college1_mlr)
```

**Multiple regression linear model:**

$y_{i}$ = 53091.45 + 0.824(tuition_avg) + 10965.41(typePublic) + 0.284(total_enrollment) + 18706.94(ivy_league)

All p-values are extremely low. $R^{2}$ = 0.555

### First Model (Residual Plots)

```{r}
#checking assumptions with residual plots, clear right skew in total_enrollment but other plots look ok 
residualPlots(college1_mlr, test = FALSE)
residualPlot(college1_mlr)
```

The residuals for tuition, type, ivy league, and the fitted model seem evenly distributed, but very far from 0. There is a lot of variation in this model. The enrollment residuals are skewed right.

### 2nd Model (log(enrollment))

```{r}
#fitting second model with natural transformation on total_enrollment
college2_mlr <- lm(mid_career_pay ~ tuition_avg + type + log(total_enrollment) + ivy_league, data = full_data)
summary(college2_mlr)
#checking assumptions with residual plots, no more skew but residuals are very large
residualPlot(college2_mlr)
residualPlots(college2_mlr)
```

$y_{i}$ = 36120 + 0.801(tuition_avg) + 9980(typePublic) + 2446(log(total_enrollment)) + 18140(ivy_league)

P-values still look good, and residual plots are not skewed. $R^{2}$ value is slightly lower at .553.

```{r}
#fitting third model with natural log on response variable as well
college3_mlr <- lm(log(mid_career_pay) ~ tuition_avg + type + log(total_enrollment) + ivy_league, data = full_data)
summary(college3_mlr)
#checking assumptions with residual plots, everything looks fine
residualPlot(college3_mlr)
residualPlots(college3_mlr)
```


### Multicollinearity?

```{r}
#using correlation matrices and VIF to check for multicolinearity, nothing concerning found
pairs(mid_career_pay ~ tuition_avg + factor(type) + log(total_enrollment) + factor(ivy_league), data = full_data)
vif(college3_mlr)
```

VIF: no values greater than 5! looks good

### Outliers?

```{r}
#using leverage and Cook's distance to look for influential points, nothing concerning found
infIndexPlot(college3_mlr, vars = "hat")
infIndexPlot(college3_mlr, vars = "Cook")
```

```{r}
#graphing the model prediction with all predictors
model_pred1 <- ggpredict(college3_mlr, terms = ~tuition_avg + type + total_enrollment)
plot(model_pred1, show_ci = FALSE) +
  labs(x = "Average Tuition",
       y = "Mid-Career Salary",
       title = "Predicted Mid-Career Salary",
       color = "Type")

#graphing model prediction just tuition vs mid-career pay
model_pred2 <- ggpredict(college3_mlr, terms = ~tuition_avg)
plot(model_pred2, show_ci = FALSE) +
  labs(x = "Average Tuition",
       y = "Estimated Mid-Career Salary",
       title = "Predicted Mid-Career Salary")

```
```{r}
#creating 95% confidence intervals for the coefficients  
confint(college3_mlr, level = 0.95)
```

